Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-10 analyses/2015_06_27_ResTime.Rmd

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/SimData.csv")  
sim.data <- subset(sim.data, motion == ' fluid ')
```

@@

@@

@@

species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/Species.csv", header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)), as.is = TRUE, skipNul = TRUE, fill = TRUE)
species.list[is.na(species.list)] <- -1
```

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/SimData.csv")  
sim.data <- subset(sim.data, motion == ' fluid ')
```

@@

## We hypothesized that the realtionship species evenness (E) to residence time would be U-shaped, and that the relationship of species turnover (B) to residence time would be L-shaped.

png(filename = '~/GitHub/hydrobide/results/figs/EandB_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

sp.lists <- c()

p1 <- ggplot(sim.data, aes(x=particle.tau, y=e.var, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Evar") +
  labs(title="Evenness") +
  guides(colour=FALSE) + 
  scale_x_log10(limits = c(10, 1000)) + 
  scale_y_log10(limits = c(100, 10000)) +
  coord_fixed(ratio = 1)

p2 <- ggplot(sim.data, aes(x=particle.tau, y=S, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Whittaker's") +
  labs(title="Species turnover") +
  guides(colour=FALSE) +
  scale_x_log10(limits = c(10, 1000)) +
  coord_fixed(ratio = .0345)

@@

source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")
source("~/GitHub/hydrobide/tools/Rbin/metrics.R")

@@

species.list <- c()
r <- 0
while(r < 61){
  print(r)
  myData <- list(read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/Species.csv", 
            header = FALSE, sep = ",",

            skip=r, nrows=1))
  species.list <- c(species.list, myData)
  r <- r + 1
  }

sim.data$species.list <- species.list
num.sims <- max(sim.data$sim) + 1

i <- 0
while (i < num.sims){

  sp.sub <- subset(sim.data$species.list, sim == i)
  sp.beta <- c()
  j <- 2
  while(j <= length(sp.sub)){
    print(j)
    w.beta <- sp.turnover(sp.sub[j], sp.sub[j-1])
    if(w.beta != -1){
      sp.beta <- c(sp.beta, w.beta)
      }
    j <- j+1
    }
  i <- i+1
  print(sp.beta)
  }
```
